\documentclass[../main/thesis.tex]{subfiles}

\begin{document}

\begin{acknowledgements}      

First of all, I would like to express my deep gratitude to my advisor, Assistant Prof. Dr. Sirirut Vanichayobon, for her support and guidance in the discussion on different opinions, for her patient and generously spent hours in correcting both my stylistic and scientific mistakes, and for a completed final research. She has helped me become better in conducting scientific research and scientific writing.

I would like to express my sincere thanks to my co-advisor, Assistant Prof. Dr. Ladda Preechaveerakul. The door to Assistant Prof. Dr. Ladda Preechaveerakul office always opens whenever I ran into a trouble spot or had a question about my study.

Besides my advisor, I would like to thank the rest of my dissertation committee: Associate Prof. Dr. Ohm Sornil and Assistant Prof. Dr. Wiphada Wettayaprasit, for their insightful comments and encouragement to accomplish my study.

My thanks go to PSU Ph.D scholarship financially supported by the Graduate School, Prince of Songkla University (PSU). I also gratefully acknowledge the PSU.GS. Financial Support for Thesis, Fiscal Year 2017 from Graduate School, PSU.

I also thank all lecturers and officers at the Department of Computer Science, Faculty of Science, PSU, who gave access to the Ph.D. office and research facilities. Without their precious supports, it would not be possible to conduct this research.

I would like to thank my friends studying in Master and Ph.D. degree at Department of Computer Science, Faculty of Science, PSU, who helped and encouraged me to overcome difficulties during my study.

Last but not least, my deepest thanks are going to my parents who always encourage me, believe in me, and give me the willpower to keep walking, and to my brother who always cheers me up and stands by me.

%Firstly, I would like to give many thanks to my advisor, Asst. Prof. Dr. Sirirut Vanichayobon, and my co-advisor, Asst. Prof. Dr. Ladda Preechaveerakul, for their support and guidance throughout my research. They helped me become better in conducting scientific researches and scientific writing.
%
%I am also thankful my colleagues at Department of Computer Science, Faculty of Science, Prince of Songkla University.


\end{acknowledgements}

\end{document}