\documentclass[../main/thesis.tex]{subfiles}

\begin{document}

\begin{vitae}
	\setlength\parindent{0cm}	\textbf{Educational Attainment}	
	\vspace{.6em} \newline
	% The column width of the table is significant.
	% The alphabet 'T' of the header 'VITAE' must be lay in the line with the alphabet 'I' of 'Institution'.
	\begin{tabular*}{\textwidth}{@{}E{.32\textwidth} E{.3\textwidth}@{} E{.3\textwidth}@{}}
	
		\textbf{Degree}	& \textbf{Name of Institution} & \textbf{Year of Graduation} \\
		
		Master of Science (Computer Science) & Prince of Songkla University & 2012 \\[1.1cm]
		Bachelor of Science (Computer Science) with first class honor & Prince of Songkla University & 2010 \\
	\end{tabular*}\vspace{.7cm}

	% Define: add heading
	% Usage: \vitaeEntries{<text>}{<item>}
	\vitaeEntries{Scholarship Awards}
	{
		% Define: add items without a bullet
		% Usage: \begin{vitaeItem} ... \end{vitaeItem}
		\begin{vitaeItem}
			\item PSU.GS financial support for thesis, Fiscal year 2017 from Graduate School, Prince of Songkla University, 2017 -- 2018.
			\item PSU-PhD scholarship from Prince of Songkla University, 2014 -- 2019.
			\item Research Assistant Scholarship supported by Faculty of Science, Prince of Songkla University, 2010 -- 2012.
		\end{vitaeItem}
	}

	\vitaeEntries{Work -- Position and Address}
	{
		\begin{vitaeItem}
			\item Lecturer at Department of Information Technology Business, Prince of Songkla University, Surat Thani campus, Surat Thani, Thailand, May 2013 -- October 2013.
			\item Lecturer at Department of Computer Science, Suratthani Rajabhat University, Surat Thani, Thailand, May 2012 -- April 2013.
		\end{vitaeItem}
	}

	\vitaeEntries{List of Publications}
	{
		% Define: add items of publications
		% Usage: \begin{pubItem} ... \end{pubItem}
		\begin{pubItem}
			\item Naphat Keawpibal, Ladda Preechaveerakul, Sirirut Vanichayobon, ``HyBiX: A Novel Encoding Bitmap Index for Space- and Time-Efficient Query Processing'', \textit{Turkish Journal of Electrical Engineering \& Computer Sciences}, Vol. 27, No. 2, 2019, pp. 1504--1522. doi: \href{https://doi.org/10.3906/elk-1807-277}{10.3906/elk-1807-277}.
			
			\item Naphat Keawpibal, Ladda Preechaveerakul, Sirirut Vanichayobon, ``Optimizing Range Query Processing for Dual Bitmap Index'', \textit{Walailak Journal of Science and Technology (WJST)}, Vol. 16, No. 2, 2019, pp. 133--142.
		\end{pubItem}
	}

	\vitaeEntries{List of Proceedings}
	{
		\begin{pubItem}
			\item Naphat Keawpibal, Jarunee Duangsuwan, Wiphada Wettayaprasit, Ladda Preechaveerakul, Sirirut Vanichayonon, ``DistEQ: Distributed Equality Query Processing on Encoded Bitmap Index'', in \textit{2015 12th International Joint Conference on Computer Science and Software Engineering (JCSSE 2015)},
			Hat Yai, Thailand, 2015, pp. 309--314. doi: \href{https://doi.org/10.1109/JCSSE.2015.7219815}{10.1109/JCSSE.2015.7219815}.
			
			\item Amorntep Keawpibal, Niwan Wattanakitrungroj, Sirirut Vanichayonon,
			``Enhanced Encoded Bitmap Index for Equality Query'', in \textit{2012 8th International Conference on Computing Technology and Information Management (NCM and ICNIT)}, Seoul, South Korea, 2012, pp. 293--298.
		\end{pubItem}
	}

\end{vitae}

\end{document}